Motion Planning and Robust Decentralized Fault-Tolerant Tracking Control of Hybrid UAVs and Biped Robots Team System for Search and Rescue Usage

### 2022-12-06 paper/paper.tex
Revise paper Section II, done

\title{Motion Planning and Robust Fault-Tolerant Control of Hybrid UAVs and Biped Robots Team System for Search and Rescue Usage}

@@

\begin{abstract}
In this study, we investigate a motion planning and robust fault-tolerant control of a hybrid UAVs and biped robots team system (URTS) for the purpose of search and rescue (S\&R). The system architecture of URTS is proposed at first to illustrate the issues to be addressed in URTS and the relationships between them. The task allocation and path planning problems are first investigated and stated. Next, we focus on the local motion planning problem for UAV flying and robot walking behavior, and then the tracking control problem for UAV and robot. The relationship between local motion planning and tracking control, the transformation of the reference trajectory, is also explored in detail. By converting the dynamics model of UAV and robot into a unified agent dynamics model, a design method for an robust $H_\infty$ decentralized observer-based feedforward-linearized PID fault-tolerant control (FTC) is proposed for the agents in URTS. A novel smoothing signal model of fault signal is embedded into the linearized system to achieve the active FTC through observer estimation. Then, the design of the robust $H_\infty$ decentralized observer-based feedforward-linearized FTC of URTS is transformed into a linear matrix inequality (LMI) -constrained optimization problem which can be solved by a two-step design procedure. With the help of MATLAB LMI Toolbox, the tracking problem of each UAV and robot in URTS is effectively solved. Finally, the simulation results are used to demonstrate the operation of URTS and to verify the effectiveness of the proposed tracking control method under the external disturbance and the actuator and sensor fault.
\end{abstract}

@@

\section{Introduction}
% unmanned vvehcile
\PARstart{I}{n} recent years, the unmanned vehicle (UV) has attracted attention due to the advances in communication technology, sensing devices, and computing power. It not only reduces labor costs and brings convenience to life, but more importantly, it can replace some dangerous jobs for humans. Due to these benefits, it has been widely used in many scenarios, such as S\&R, battlefield, logistics and transportation, surveillance, etc \cite{9700861}. Compared with a single UV, multiple UVs can perform more complex tasks and are more robust due to a large number of agents \cite{8352646}. However, the cost is that the design of such a multi-agent system (MAS) becomes more intricate as there are more problems to be resolved, such as formation, collision avoidance between agents, task allocation, and cooperation between agents \cite{chen2019control}. In addition to the number increasment, a heterogeneous multi-agent system (HMAS) combining various types of UV is also valued \cite{9371292}. Compared with homogeneous multi-agent system, it can adapt to a wider variety of application scenarios because each agent has different aptitudes.

To construct an unmanned HMAS, the three required key capabilities are perception, decision-making and control. Perception is to obtain information through the sensor (e.g., localization or computer vision), decision-making is to make decisions through the sensor information, and control is to execute the decision through the actuator. To limit the scope of this paper, we focus on decision-making and control problem only. Three main problems of decision-making in an unmanned HMAS are task allocation, path planning and collision avoidance. Task allocation is to optimally assign tasks to each agent under some constraints such as agent capabilities, fuel cost, time cost, etc \cite{skaltsis2021survey}. Path planning is to optimally plan paths for each agent while subject to constraints such as agent kinodynamic properties, distance, obstacles collision, etc \cite{zhang2018path}. Collision avoidance is to avoid collision with obstacles. Although collision avoidance is often concerned in path planning, the collision avoidance system is also independently studied because of the requirements for the safety and reliability of the actual system \cite{9108245}.

@@

To the best of the authors' knowledge, most of the literature focus on only one specific problem in such an unmanned multi-agent S\&R system, such as task allocation problem, path planning problem or control problem. Additionally, few literatures illustrate the relationship between these problems. This leads us to propose a system architecture of hyibrid UAVs and biped robots team system (URTS) for S\&R usage. The flowchart of decision-making and control process of URTS is also given. We divide it into five main hierarchical processes, i.e., task allocation, path planning, behavior layer, local motion planning and tracking control. It is because the URTS needs to be able to assign different tasks to agents to perform first. After a task is assigned, if the task is to reach a goal location, a path to reach it needs to be planned. To make agent move on the path, a behavior corresponding to the environment is required to determine. Then, a local motion corresponding to the behavior of the agent needs to be designed. Finally, a controller must be designed to track the trajectory of the motion. In order to further limit the scope of the study, we will focus on the latter two processes. But to illustrate how the whole system works, the first three problems are also briefly stated.

@@

Besides, the formation control is also a topic in MAS \cite{wang2022consensus}. Its purpose is to keep a MAS in a formation while moving. Although formation control provides a simple framework for the control of a large number of agents, considering the complexity of the disaster relief environment, formation will make the application of URTS inflexible. It is because we expect that agents in URTS need to organize multiple teams of different scales and types to deal with multiple tasks of different scales and types in a disaster relief environment. In this situation, it is more reasonable to treat each agent as an independent individual and specify an independent trajectory for each agent to follow.

In order to cope with the fault in the actual system, the fault-tolerant control (FTC) has also been widely studied. According to the way of handling the fault, it can be divided into the passive FTC and the active FTC \cite{6669235}. The passive FTC treats the fault as an unknown system perturbation and designs a control law to tolerate it. In contrast, the active FTC will first estimate and identify the fault and then compensate it through the controller. Despite the added complexity in controller design, the active FTC will outperform the passive FTC due to the extra estimation steps. Based on the foregoing, a robust $H_\infty$ decentralized observer-based feedforward-linearized FTC is proposed to deal with the control problem in URTS.
% The control problem of UAV has been widely studied due to its applicability and low cost (cite: uav control).
% the control problem of robot

The contributions of this study are described as follows:
\begin{enumerate}
    \item A system architecture and system flow of URTS for the purpose of S\&R are proposed so that the issues involved in URTS and their relationships can be defined and resolved.
    \item A transformation between the trajectory generated by the path planning algorithm and the trajectory required for tracking control design is proposed to enable some common path planning algorithms can be applied to the tracking control of agents in URTS.
    \item A general agent dynamics model is proposed so that the robust $H_\infty$ decentralized observer-based tracking control problems of the heterogeneous agents in URTS, UAVs and biped robots, can be solved together.
\end{enumerate}

The remainder of the paper is organized as follows. In Section II, a system architecture of URTS in S\&R usage is proposed and the function and relationship of its components, i.e., task allocation, path planning, behavior layer, local motion planning and tracking control are described. In Section III, the system model of agents in URTS are given to design the motion of UAV flying and biped robot walking behavior and the control strategy of agents. In Section IV, a robust $H_\infty$ decentralized observer-based feedforward-linearized FTC is proposed for the agents in URTS with the help of a general agent dynamics model. In Section V, a simulation example is given to illustrate the operation of the system architecture of URTS and to verify the effectiveness of the proposed tracking control method. In Section VI, a conclusion is maded.

@@

\section{PRELIMINARIES OF URTS in S\&R usage}
The URTS will start with a given S\&R area, and end with mission completed. The URTS is composed of $N_T$ teams and a ground station. Each team contains $N_A$ agents with $1$ UAV and $N_A-1$ robots. Hence, the $j$th agent in the $i$th team is denoted as $\alpha_{i,j}$, where $i=1,2,...,N_T$ and $j=1,2,...,N_A$. The UAVs are chosed as the first agents in each team, i.e., $\alpha_{i,1}$. Each agent has environmental sensing capability and load capability, while the ground station is responsible for computing and decision-making. Besides, there are communication channels between agents and ground station through wireless network.
% The system architecture if URTS is shown in Fig. \ref{fig:1}.
% \begin{figure}[htbp]
% \centering
% \includegraphics[width=0.4\textwidth]{fig/1.pdf}\caption{System structure of URTS}%
% \label{fig:1}
% \end{figure}

@@

If a task is to reach a location of certain goal, we need to find a collision-free path to reach it. 
% there must exist multiple feasible paths. Similar to task allocation, we usually want to find an optimal path. 
% Besides, it's necessary to concern about collision between agents or between agents and obstacles in the actual scenario, 
Hence, each agent will also sense distance-related information about its surrounding and send it back to the ground station. The ground station will combine this information with the goal location assigned by task allocation algorithm and make a decision to avoid obstacles and other agents nearby.
% That is, the path of each agent will be reassigned every moment if needed by solving the dynamic path planning problems.

@@

\subsection{Task Allocation}
In the URTS, it can be expected that each agent $\alpha_{i,j}$ will be assigned several specific tasks, such as searching a specific area, or delivering supplies to disaster area, etc. However, the number of agents and tasks is more than one, and each agent has different capabilities (e.g., moving speed or load capacity) and status (e.g., their own position or the amount of supplies carried), and each task has different characteristics (e.g., urgency, position, amout of supplies needed). Therefore, the results of task allocation can be "good or bad", which leads us to find the optimal allocation. This problem is referred to a task allocation problem or multi-robot task allocation problem. A problem formulation and a mathematical model of problem can be found in \cite{khamis2015multi}. Although many different formulations and models have been employed to solve the task allocation problem, the common goal is to find a set of agent-task pairs to achieve a specific cost function. In this paper, we assume that the tasks have been properly assigned so that every agent knows a destination $q_{goal}$ it needs to go at every moment.
% $(\mathcal{G})_n, n\in\mathbb{Z}\cap[1, N], N\in\mathbb{Z}^+$
\textit{
    \begin{remark}
        This block is like a commander since it is used to assign task for agents. Thus, if the real S\&R system has human experts as commanders, he can replace its job or make decisions together with it to maximize the rescue value.
    \end{remark}
}
\textit{
    \begin{remark}
        Although each agent has its own team, agents can also work across teams. For example, if the result given by the task allocation algorithm contains the agent-task pairs $(\alpha_{1,5},T_1)$ and $(\alpha_{2,2},T_1)$, then the agent $\alpha_{1,5}$ in team 1 and the agent $\alpha_{2,2}$ in team 2 will execute task $T_1$ together. 
    \end{remark}
}

\subsection{Path Planning}
After a destination $q_{goal}$ is assigned for each agent, next step is to find a collision-free path from current position to it. There must exist multiple feasible paths to go. Similar to task allocation, we usually want to find an optimal path. There are several path planning algorithm to handle this problem. Due to the developmental and universal nature of roadmap-based path planning algorithm, this paper considers it as the path planning method of URTS. This method attempts to discretize the search space into interconnected roads and find the path on it. 
% According to the roadmap construction method, it can be divided into deterministic and sample-based.

@@

Furthermore, the constraints imposed by the mechanical structure are needed to consider within pathfinding process mentioned by other literatures but it will be left to local motion planning block to deal with. The reason is that URTS works on a complex environment and therefore requires a variety of behaviors to respond, and different behaviors have different constraints (e.g., curvature constraints between running and walking behavior are expected to be different for robot). In this case, a unified planner will become overly complex and impracticable. Therefore, we divide path planning into three subprocesses, i.e., path planning, behavior layer and local motion planning. The path planning block becomes a global planner and regard an agent as a point without kinodynamic constraints. The local motion planning block becomes a local planner and consider the motion planning of a specific behavior.
% In this case, the configuration space $\mathcal{C}$ degenerates to $\mathbb{R}^3$.

@@

\subsection{Behavior Layer}
% Since UAVs and robots are real physical systems, they must interact with the environment through a behavior so that they can move and act in the physical world.
Path planning tells agents where to go but not how since we regard the agent as a point. Taking robot as an example, it may walk, run, climb, or jump to follow the path $(\sigma_n)$ in real scenario. These behaviors with changing position are classified as "moving" behavior in this paper. Besides, the agents in the hybrid URTS do not always moving. Somtimes they have to suspend to take an action (e.g., getting and putting supplies, rotating in place to collect more environment information) or deal with some unexpected situations (e.g., no path found, the robot falls). These behaviors without changing position are classified as "action" behavior in this paper. More behaviors can be added so that the agent can have more ways to act with environment but there must have a corresponding behavior every moment otherwise the agent will lose control. The sequence of these behaviors can be expressed as:
\begin{equation}
    (\beta_n), n\in\mathbb{Z}\cap[1,k_f], \beta_n\in\mathcal{B}
\end{equation}
where $\mathcal{B}$ is the set of behaviors. It is to say that the path $(\sigma_n)$ is divided into many segments and each segment corresponds to a specific behavior. By the object information in Fig. \ref{fig:sys}, an appropriate behavior can be judged. However, it will be a rather complicated project, so this article only gives the structure of the behavior set. The behavior set $\mathcal{B}$ of agent in URTS can be roughly discribed in Fig. \ref{fig:behavior}.

@@

\subsection{Local Motion Planning}
After a specific behavior is determined, the next step is to design a motion to achieve that behavior. Local motion planning block is like path planning block but its scale is smaller and its resolution and precision must be higher. Collision checking is needed since we consider agent as a point in path planning block and it is a real mechanical body here. Furthermore, the kinodynamic constraint is handled in this block. Although motion planning and path planning are separated into two blocks, the technologies involved are similar and often with the same notion in other literature. Therefore, the output of this block is also a path $r[k]$. The flowchart of local motion planning block is shown in Fig. \ref{fig:LocalMotionPlanning}
\begin{figure*}[htbp]
    \centering
    \includegraphics[scale=.12]{fig/LMP.png}\caption{The flowchart of local motion planning. The corresponding motion planning will be executed according to the behavior determined by the behavior layer. The exception terminator in figure represents an exceptional condition that performs unconsidered behaviors. The reference path $r[k]$ is a sequence (or say a discrete signal) designed by a specific behavior block.}
    \label{fig:LocalMotionPlanning}
\end{figure*}

In Fig. \ref{fig:LocalMotionPlanning}, some basic behaviors of UAV and robot mentioned before are added to illustrate the flow of this block. To limit the scope of this article, we only focus on the motion planning of flying behavior of UAV and walking behavior of robot. They are belong to moving behavior in Fig. \ref{fig:LocalMotionPlanning}. A more detailed description will be given in the next section.

\subsection{Tracking Control}
To analysis the control problem in the continuous time domain, $r[k]$ will first convert to a continuous signal by D/A convertor with a timescale, i.e., sampling period. By analyzing the dynamic model of each agent, a desired reference trajectory $r(t)$ is designed. $r(t)$ describes the position and orientation that need to be reached over time by a machine system governed by a dynamic equation. Note that the path and trajectory are distinguished in some literature. Different from path (e.g., $(\sigma_n)$ or $r[k]$), a trajectory $r(t)$ has considered the time in physic world. We also distinguish in this way in this article.

If each agent in hybrid URTS can track each own reference trajectory $r(t)$, then they can move in the physical world as we expect. To this end, a control method need to be design. It will be discussed detailly in Section IV. In addition, the sensing information collected by the sensors in this block is not only used for control but also sent back to the upper layer as shown in Fig. \ref{fig:sys}.

\section{system description of UAVs and biped robots in URTS}
In order to design a reference trajectory $r(t)$ for the motion of UAV and robot, their dynamic models must be given first. After the system description of UAV and robot, the motion planning of flying and walking as shown in Fig. \ref{fig:FandW} will be discussed subsequently and separately in the next two subsections.
\begin{figure*}[htbp]
    \centering
    \includegraphics[scale=.12]{fig/FandW.png}\caption{The flowchart of Flying and Walking. In both blocks, a smoothed path is obtained by post-processing first. Then the respective motion of behavior is designed. The final outputs of Flying and Walking are all desired reference path $r[k]$, but its value and dimension will vary according to the dimension of the system model.}
    \label{fig:FandW}
\end{figure*}
Before the discussion of the motion planning of these two behaviors, the following assumption is maded.
\textit{
    \begin{assumption} \label{asm:cc again}
        The space between obstacles is large enough to eliminate the need for collision checking again, and the average speed of agents is slow enough to ignore dynamic constraints
    \end{assumption}
}
However, for these two behaviors, there exists an inevitable kinematic constraint on the curvature of local motion. Although an accurate reference trajectory without breaking the curvature constraint can be designed, it is not easy to solve this problem. Additionally, it is not nessasry for these two behaviors in URTS since they are uesd to move from one location to another while the effect of error during moving caused by breaking the curvature constraint is relatively insignificant. At the same time, the \textit{Assumption \ref{asm:cc again}} makes sure the error will not cause collision. As an alternative, this problem can be handled by curve fitting which can be regarded as a post-process of the path $(\sigma_n)$. The post-process will appear in the begining of motion planning process of these two behaviors as shown in Fig. \ref{fig:FandW}.

@@

The design procedure of the optimal $H_\infty$ decentralized observer-based feedforward-linearized FTC scheme for each agent in (\ref{eq:agent d1}) is summarized as follows:
\begin{enumerate}
    \item Apply the feedforward control in (\ref{eq:control}) to obtain the linearized tracking error dynamic system (\ref{eq:error})
    \item Construct the smoothing signal models (\ref{eq:smooth model}) for the actuator fault $f_1(t)$ and sensor fault $f_2(t)$. Embed into the linearized system (\ref{eq:error}) to get the augmented tracking error system (\ref{eq:e_bar}).
    \item Construct the robust FTC law (\ref{eq:u_fb}) and the augmented estimation error system (\ref{eq:e_tilde}) to obtain the augmented tracking and estimation error system in (\ref{eq:x_tilde})
    \item Solve the LMIs-constrained optimization problem (\ref{LMI constraint}) by the two-step design to obtain the control gain $K$ and observer gain $L=P_2^{-1}Y_2$ for each agent in the hybrid URTS.
\end{enumerate}

@@

For further verification, we visualized the simulation of a hybrid team tracking in URTS and the configuration trajectory of biped robot on the online resource \cite{mySimulation}. The results again demonstrate the effectiveness of the proposed $H_\infty$ decentralized observer-based feedforward-linearized FTC method for agents in URTS.

>>>>

\title{Motion Planning and Robust Decentralized Fault-Tolerant Tracking Control of Hybrid UAVs and Biped Robots Team System for Search and Rescue Usage}

@@

\begin{abstract}
In this study, we investigate a motion planning and robust fault-tolerant control of a hybrid UAVs and biped robots team system (URTS) for the purpose of search and rescue (S\&R). The system architecture of URTS is proposed at first to illustrate the issues to be addressed in URTS and the relationships between them. The task allocation and path planning problems are first investigated. Next, we focus on the local motion planning problem for UAV flying and robot walking behavior, and then the tracking control problem for UAVs and robots in the hybrid team system. The relationship between local motion planning and tracking control, i.e., the transformation of the reference trajectory, is also explored in detail. By converting the dynamics models of UAV and robot into a unified agent dynamics model, the robust $H_\infty$ decentralized observer-based feedforward fault-tolerant control (FTC) strategy is proposed for the agents in URTS. A novel smoothing signal model of fault signal is embedded into the linearized system to achieve the active FTC through observer estimation. Then, the design of the robust $H_\infty$ decentralized observer-based feedforward FTC strategy of URTS is transformed into a linear matrix inequality (LMI) -constrained optimization problem of each agent in the hybrid team system which can be solved by a two-step design procedure. With the help of MATLAB LMI Toolbox, the $H_\infty$ decentralized fault-tolerant tracking problem of each UAV and robot in URTS is effectively solved. Finally, the simulation results are used to demonstrate the operation of URTS and to verify the effectiveness of the proposed $H_\infty$ decentralized fault-tolerant tracking control method of hybrid URTS under the external disturbance and the actuator and sensor fault.
\end{abstract}

@@

\section{Introduction}
% unmanned vvehcile
\PARstart{I}{n} recent years, the unmanned vehicle (UV) has attracted attention due to the advances in communication technology, sensing devices, and computing power. It not only reduces labor costs and brings convenience to life, but more importantly, it can replace some dangerous jobs for humans. Due to these benefits, it has been widely used in many scenarios, such as S\&R, battlefield, logistics and transportation, surveillance, etc. \cite{9700861}. Compared with a single UV, multiple UVs can perform more complex tasks and are more robust due to a large number of agents \cite{8352646}. However, the cost is that the design of such a multi-agent system (MAS) becomes more intricate as there are more problems to be resolved, such as formation, collision avoidance between agents, task allocation, and cooperation between agents \cite{chen2019control}. In addition to the number increasment, a heterogeneous multi-agent system (HMAS) combining various types of UV is also valued \cite{9371292}. Compared with homogeneous multi-agent system, it can adapt to a wider variety of application scenarios because each agent has different aptitudes.

To construct an unmanned HMAS, the three required key capabilities are perception, decision-making and control. Perception is to obtain information through the sensor (e.g., localization or computer vision), decision-making is to make decisions through the sensor information, and control is to execute the decision through the actuator. To limit the scope of this paper, we focus on decision-making and control problem only. Three main problems of decision-making in an unmanned HMAS are task allocation, path planning and collision avoidance. Task allocation is to optimally assign tasks to each agent under some constraints such as agent capabilities, fuel cost, time cost, etc. \cite{skaltsis2021survey}. Path planning is to optimally plan paths for each agent while subject to constraints such as agent kinodynamic properties, distance, obstacles collision, etc. \cite{zhang2018path}. Collision avoidance is to avoid collision with obstacles. Although collision avoidance is often concerned in path planning, the collision avoidance system is also independently studied because of the requirements for the safety and reliability of the actual system \cite{9108245}.

@@

To the best of the authors' knowledge, most of the literature focus on only one specific problem in such an unmanned multi-agent S\&R system, such as task allocation problem, path planning problem or control problem. Additionally, few literatures illustrate the relationship between these problems. This leads us to propose a system architecture of hyibrid UAVs and biped robots team system (URTS) for S\&R usage. The flowchart of decision-making and control process of URTS is also given. We divide it into five main hierarchical processes, i.e., (i) task allocation, (ii) path planning, (iii) behavior layer, (iv) local motion planning and (v) tracking control. It is because the URTS needs to be able to assign different tasks to agents to perform first. After a task is assigned, if the task is to reach a goal location, a path to reach it needs to be planned. To make agent move on the path, a behavior corresponding to the environment is required to be determined. Then, a local motion corresponding to the behavior of the agent needs to be designed. Finally, a controller must be designed to track the trajectory of the motion. In order to further limit the scope of the study, we will focus on the latter two processes. But to illustrate how the whole system works, the first three problems are also briefly stated.

@@

Besides, the formation control is also a topic in MAS \cite{wang2022consensus}. Its purpose is to keep a MAS in a formation while moving. Although formation control provides a simple framework for the control of a large number of agents, considering the complexity of the disaster relief environment, formation will make the application of URTS inflexible. It is because we expect that agents in URTS need to organize multiple teams of different scales and types to deal with multiple tasks of different scales and types in a disaster relief environment. In this situation, it is more reasonable to treat each agent in URTS as an independent individual to follow a specific trajectory to form a team formation
and specify an independent trajectory for each agent to follow.

In order to cope with the fault in the actual system, the fault-tolerant control (FTC) has also been widely studied. According to the way of handling the fault, it can be divided into the passive FTC and the active FTC \cite{6669235}. The passive FTC treats the fault as an unknown system perturbation and designs a control law to tolerate it. In contrast, the active FTC will first estimate and identify the fault and then compensate it through the controller. Despite the extra complexity in controller design, the active FTC will outperform the passive FTC due to the extra estimation steps. Based on the foregoing, a robust $H_\infty$ decentralized observer-based feedforward FTC is proposed to deal with the control problem in hybrid URTS.
% The control problem of UAV has been widely studied due to its applicability and low cost (cite: uav control).
% the control problem of robot

The contributions of this study are described as follows:
\begin{enumerate}
    \item A system architecture and system flow of hybrid URTS for the purpose of S\&R are proposed so that the issues involved in hybrid URTS and their relationships can be defined and resolved.
    \item A transformation between the trajectory generated by the path planning algorithm and the trajectory required for tracking control design is proposed to enable some common path planning algorithms can be applied to the team formation tracking control of agents in hybrid URTS.
    \item A general agent dynamics model is proposed so that the robust $H_\infty$ decentralized observer-based fault-tolerant tracking control problems of the heterogeneous agents in URTS, UAVs and biped robots, can be solved together.
\end{enumerate}

The remainder of the paper is organized as follows. In Section II, a system architecture of URTS in S\&R usage is proposed and the function and relationship among its components, i.e., task allocation, path planning, behavior layer, local motion planning and tracking control are described. In Section III, the dynamics models of agents in URTS are given to design the motion of UAV flying and biped robot walking behavior and the control strategy of agents. In Section IV, a robust $H_\infty$ decentralized observer-based feedforward FTC is proposed for the agents in URTS with the help of a general agent dynamics model. In Section V, a simulation example is given to illustrate the operation of the system architecture of URTS and to verify the effectiveness of the proposed tracking control method. In Section VI, a conclusion is maded.

@@

\section{PRELIMINARIES OF URTS in S\&R usage}
The URTS will start with a given S\&R area, and end with mission completed. The URTS is composed of $N_T$ teams and a ground station. Each team contains $N_A$ agents with $1$ UAV and $N_A-1$ robots. Hence, the $j$th agent in the $i$th team is denoted as $\alpha_{i,j}$, where $i=1,2,...,N_T$ and $j=1,2,...,N_A$. The UAVs are chosed as the first agents in each team, i.e., $\alpha_{i,1},i=1,2,\dots,N_T$. Each agent has environmental sensing capability and load capability, while the ground station is responsible for computing and decision-making. Besides, there are communication channels between agents and ground station through wireless network.
% The system architecture if URTS is shown in Fig. \ref{fig:1}.
% \begin{figure}[htbp]
% \centering
% \includegraphics[width=0.4\textwidth]{fig/1.pdf}\caption{System structure of URTS}%
% \label{fig:1}
% \end{figure}

@@

If a task is to reach a location of certain goal, we need to find a collision-free path to reach it. 
% there must exist multiple feasible paths. Similar to task allocation, we usually want to find an optimal path. 
% Besides, it's necessary to concern about collision between agents or between agents and obstacles in the actual scenario, 
Hence, each agent will also sense distance-related information about its surrounding and send it back to the ground station. The ground station will combine this information with the goal location assigned by task allocation algorithm and then make a decision to avoid obstacles and other agents nearby.
% That is, the path of each agent will be reassigned every moment if needed by solving the dynamic path planning problems.

@@

\subsection{Task Allocation}
In the URTS, it can be expected that each agent $\alpha_{i,j}$ will be assigned to several specific tasks, such as searching a specific area, or delivering supplies to disaster area, etc. However, the number of agents and tasks is more than one, and each agent has different capabilities (e.g., moving speed or load capacity) and status (e.g., their own position or the amount of supplies carried), and each task has different characteristics (e.g., urgency, position, amout of supplies needed). Therefore, the results of task allocation can be "good or bad", which leads us to finding the optimal allocation. This problem is referred to a task allocation problem or multi-robot task allocation problem. A problem formulation and a mathematical model of problem can be found in \cite{khamis2015multi}. Although many different formulations and models have been employed to solve the task allocation problem, the common goal is to find a set of agent-task pairs to achieve a specific cost function. In this paper, we assume that the tasks have been properly assigned so that every agent knows a destination $q_{goal}$ it needs to go at every moment.
% $(\mathcal{G})_n, n\in\mathbb{Z}\cap[1, N], N\in\mathbb{Z}^+$
\textit{
    \begin{remark}
        This block is like a commander since it is used to assign task for agents. Thus, if the real S\&R system has human experts as commanders, he can replace its job or make decisions together with it to maximize the rescue value.
    \end{remark}
}
\textit{
    \begin{remark}
        Although each agent has its own team, agents can also work across teams. For example, if the result given by the task allocation algorithm contains the agent-task pairs $(\alpha_{1,5},T_1)$ and $(\alpha_{2,2},T_1)$, then the agent $\alpha_{1,5}$ in team 1 and the agent $\alpha_{2,2}$ in team 2 will execute task $T_1$ together. 
    \end{remark}
}

\subsection{Path Planning}
After a destination $q_{goal}$ is assigned for each agent, next step is to find a collision-free path from current position to it. There must exist multiple feasible paths to go. Similar to task allocation, we usually want to find an optimal path. There are several path planning algorithms to handle this problem. Due to the developmental and universal nature of roadmap-based path planning algorithm, this paper considers it as the path planning method of URTS. This method attempts to discretize the search space into interconnected roads and find the path on it. 
% According to the roadmap construction method, it can be divided into deterministic and sample-based.

@@

Furthermore, the constraints imposed by the mechanical structure are needed to consider within pathfinding process mentioned by other literatures but it will be left to local motion planning block to deal with. The reason is that URTS works on a complex environment and therefore requires a variety of behaviors to respond, and different behaviors have different constraints (e.g., curvature constraints between running and walking behavior are expected to be different for robots). In this case, an unified planner will become overly complex and impracticable. Therefore, we divide path planning into three subprocesses, i.e., path planning, behavior layer and local motion planning. The path planning block becomes a global planner and regards an agent as a point without kinodynamic constraints. The local motion planning block becomes a local planner and considers the motion planning of a specific behavior.
% In this case, the configuration space $\mathcal{C}$ degenerates to $\mathbb{R}^3$.

@@

\subsection{Behavior Layer}
% Since UAVs and robots are real physical systems, they must interact with the environment through a behavior so that they can move and act in the physical world.
Path planning tells agents where to go but not how since we regard the agent as a point. Taking robot as an example, it may walk, run, climb, or jump to follow the path $(\sigma_n)$ according to real scenario. These behaviors with changing position are classified as "moving" behavior in this paper. Besides, the agents in the hybrid URTS do not always moving. Somtimes they have to suspend to take an action (e.g., getting and putting supplies, rotating in place to collect more environment information) or deal with some unexpected situations (e.g., no path found, the robot falls). These behaviors without changing position are classified as "action" behavior in this paper. More behaviors can be added so that the agent can have more ways to act with environment but there must have a corresponding behavior every moment otherwise the agent will lose control. The sequence of these behaviors can be expressed as:
\begin{equation}
    (\beta_n), n\in\mathbb{Z}\cap[1,k_f], \beta_n\in\mathcal{B}
\end{equation}
where $\mathcal{B}$ is the set of behaviors. It means that the path $(\sigma_n)$ is divided into many segments and each segment corresponds to a specific behavior. By the object information in Fig. \ref{fig:sys}, an appropriate behavior can be judged. However, it will be a rather complicated project, so this article only gives the structure of the behavior set. The behavior set $\mathcal{B}$ of agent in URTS can be roughly discribed in Fig. \ref{fig:behavior}.

@@

\subsection{Local Motion Planning}
After a specific behavior is determined, the next step is to design a motion to achieve the specific behavior. Local motion planning block is like path planning block but with smaller scale and higher resolution and precision. Collision checking is needed since we consider agent as a point in path planning block but it is a real mechanical body here. Furthermore, the kinodynamic constraint is handled in this block. Although motion planning and path planning are separated into two blocks, the technologies involved are similar and often with the same notion in other literature. Therefore, the output of this block is also a path $r[k]$. The flowchart of local motion planning block is shown in Fig. \ref{fig:LocalMotionPlanning}
\begin{figure*}[htbp]
    \centering
    \includegraphics[scale=.12]{fig/LMP.png}\caption{The flowchart of local motion planning. The corresponding motion planning will be executed according to the behavior determined by the behavior layer. The exception terminator in figure represents an exceptional condition that performs unconsidered behaviors. The reference path $r[k]$ is a sequence (or say a discrete signal) designed by a specific behavior block.}
    \label{fig:LocalMotionPlanning}
\end{figure*}

In Fig. \ref{fig:LocalMotionPlanning}, some basic behaviors of UAV and robot mentioned before are given to futher illustrate the flow of this block. To limit the scope of this article, we only focus on the motion planning of flying behavior of UAV and walking behavior of robot. They are belong to the moving behavior in Fig. \ref{fig:LocalMotionPlanning}. A more detailed description will be given in the next section.

\subsection{Tracking Control}
To analyze the control problem in the continuous time domain, $r[k]$ will be first converted to a continuous signal by D/A convertor with a timescale, i.e., sampling period. By analyzing the dynamic model of each agent, a desired reference trajectory $r(t)$ is designed. $r(t)$ describes the position and orientation that need to be reached over time by a machine system governed by a dynamic equation. Note that the path and trajectory are distinguished in some literature. Different from path (e.g., $(\sigma_n)$ or $r[k]$), a trajectory $r(t)$ has considered the time in physic world. We also distinguish them in this way in this article.

If each agent in hybrid URTS can track each own reference trajectory $r(t)$, then they can move in the physical world as we expect. To this end, a control method needs to be designed. It will be discussed detailly in Section IV. In addition, the sensing information collected by the sensors in this block is not only used for control but also sent back to the upper layer as shown in Fig. \ref{fig:sys}.

\section{system description of UAVs and biped robots in URTS}
In order to design a reference trajectory $r(t)$ for the motion of UAV and robot, their dynamic models must be given first. After the system description of UAV and robot in URTS, the motion planning of flying and walking as shown in Fig. \ref{fig:FandW} will be discussed subsequently and separately in the next two subsections.
\begin{figure*}[htbp]
    \centering
    \includegraphics[scale=.12]{fig/FandW.png}\caption{The flowchart of Flying and Walking. In both blocks, a smoothed path is obtained by post-processing first. Then the respective motion of behavior is designed. The final outputs of Flying and Walking are all desired reference path $r[k]$, but its value and dimension will vary according to the dimension of the system model.}
    \label{fig:FandW}
\end{figure*}
Before the discussion of the motion planning of these two behaviors, the following assumption is maded.
\textit{
    \begin{assumption} \label{asm:cc again}
        The space between obstacles is large enough to eliminate the need for collision checking again, and the average speed of agents is slow enough to ignore dynamic constraints
    \end{assumption}
}
However, for these two behaviors, there exists an inevitable kinematic constraint on the curvature of local motion. Although an accurate reference trajectory without breaking the curvature constraint can be designed, it is not easy to solve this problem. Additionally, it is not nessasry for these two behaviors in URTS since they are uesd to move from one location to another while the effect of error during moving caused by breaking the curvature constraint is relatively insignificant. At the same time, the \textit{Assumption \ref{asm:cc again}} makes sure the error will not cause collision. As an alternative, this problem can be handled by curve fitting which can be regarded as a post-process of the path $(\sigma_n)$. The post-process will appear in the begining of motion planning process of these two behaviors as shown in Fig. \ref{fig:FandW}.

@@

The design procedure of the optimal $H_\infty$ decentralized observer-based feedforward FTC scheme for each agent in (\ref{eq:agent d1}) is summarized as follows:
\begin{enumerate}
    \item Apply the feedforward control in (\ref{eq:control}) to obtain the linearized tracking error dynamic system (\ref{eq:error})
    \item Construct the smoothing signal models (\ref{eq:smooth model}) for the actuator fault $f_1(t)$ and sensor fault $f_2(t)$. Embed into the linearized system (\ref{eq:error}) to get the augmented tracking error system (\ref{eq:e_bar}).
    \item Construct the robust FTC law (\ref{eq:u_fb}) and the augmented estimation error system (\ref{eq:e_tilde}) to obtain the augmented tracking and estimation error system in (\ref{eq:x_tilde})
    \item Solve the LMIs-constrained optimization problem (\ref{LMI constraint}) by the two-step design to obtain the control gain $K$ and observer gain $L=P_2^{-1}Y_2$ for each agent in the hybrid URTS.
\end{enumerate}

@@

For further verification, we visualized the simulation of a hybrid team tracking in URTS and the configuration trajectory of biped robot on the online resource \cite{mySimulation}. The results again demonstrate the effectiveness of the proposed $H_\infty$ decentralized observer-based feedforward FTC method for agents in URTS.
